The imprint of global magma oceans on exoplanet demographics

### 2023-02-22 src/tex/ms.tex
add a zoom-out sentence

\section{Discussion}\label{sec:discussion}
\todo[inline]{\textbf{Potential discussion points: }\\
How close is Earth to runaway? Could anthropogenic climate change push us over the edge? (-> \citet{Goldblatt2012}; what is the max. expected change in Earth's albedo due to deglaciation?}

@@

%\begin{acknowledgments}
%The authors thank Yann Fabel, Paul Molliere, Matthew Murphy, and Terry-Ann Suer for insightful discussions.
%We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
%\end{acknowledgements}

>>>>

\section{Discussion}\label{sec:discussion}
\todo[inline]{\textbf{Potential discussion points: }\\
(How close is Earth to runaway? Could anthropogenic climate change push us over the edge? (-> \citet{Goldblatt2012,Popp2016}; what is the max. expected change in Earth's albedo due to deglaciation?)}

@@

The habitable zone is widely employed in target prioritization for exoplanet missions, and it will provide context for interpreting potential signatures of life.
As we have demonstrated, it appears realistic that an empirical confirmation of the habitable zone concept is imminent.
This will be a key contribution to the search for extraterrestrial life in the Universe.

%\begin{acknowledgments}
%The authors thank Yann Fabel, Paul Molliere, Gijs Mulders, Matthew Murphy, and Terry-Ann Suer for insightful discussions.
%We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
%\end{acknowledgments}
